Plant species traits and growth rates: meta-analysis shows correlations change with plant size as predicted

### 2015-05-06 MS.tex
Import latest from overleaf

\documentclass[a4paper]{article}\usepackage[]{graphicx}\usepackage[]{color}
\usepackage{alltt}
\usepackage{amssymb,amsmath}
\usepackage{palatino}
\usepackage{framed}
\usepackage{parskip}
\usepackage{graphicx}
\usepackage{fixltx2e}
\usepackage[default,osfigures,scale=0.95]{opensans}
\usepackage{geometry}
\usepackage{longtable}
\usepackage{authblk}
\usepackage[colorinlistoftodos]{todonotes}
\geometry{verbose,tmargin=2cm,bmargin=2cm,lmargin=2cm,rmargin=2.5cm}
\linespread{1.5}

@@

May we please raise with you an issue about the literature cited? (It need not affect the review process.) We strongly believe that authors whose data publications enter into meta-analyses deserve to get credit via citation. But because of the restriction on citations in the main text, these citations are in appendices in the current draft, rather than in the main list of Literature Cited. We hope you may have a solution to situations of this kind? We understand some journals now make provision for literature cited in appendices or supp info to be scanned by ISI and other cite-counting agencies? Or perhaps the restrictions on number of papers cited can be relaxed for meta-analyses?

@@

\textbf{Keywords (8/10)} asymptotic maximum height, maximum photosynthetic rate, plant ontogenetic stage, plant functional traits, plant growth strategy, seed mass, specific leaf area, wood density

\textbf{Type of article} Letters

\textbf{Number of words in the abstract} 148

\textbf{Number of words in the main text (excluding abstract, acknowledgements, references, table and figure legends)}

\textbf{Number of words in each text box} 0

\textbf{Number of general references}

\textbf{Number of data source references} 108

\textbf{the number of figures} 2

\textbf{the number of tables} 0

\textbf{the number of text boxes} 0

\textbf{the name and complete mailing address (including telephone and fax numbers and e-mail address) of the person to whom correspondence should be sent}

\todo[inline,color=white]{Tentatively for Ecology Letters [length limits: maximum of 5000 words (main text), 2/6 figures, tables or boxes, and 64/50 references.] (4667 word  /5000)}

\todo[inline,color=white]{1. need to delete references 57/50}

@@

\todo[inline,color=white]{3. the bibliography style needs to be changed to fit with the new style of Ecology letters: journal abbreviation}

\todo[inline, color=white] {4. to re write Appendix A growth equation : do we keep equation? information about plant size?}

\todo[inline, color=white] {5. to write a "Read.me" file for the dataset/guithub}

\todo[inline, color=white] {6. to add the list of traits/stage categoreis combiation for which we identified a need of more data in the last paragrph of the discussion: DONE}

@@

@@

The phrase "plant ecological strategy" refers to how species face the challenge they all share:  to acquire sufficient water, nutrients and light for individual growth and to live long enough to replace themselves with offspring. An idea that strategy differences might involve fast vs slow growth goes back at least to Grime and Hunt \citeyearpar{Grime:1975gr}, who measured a wide spread of relative growth rates for seedlings during early exponential growth under favourable conditions. Seedling potential RGR has continued to be used as a major strategy indicator within the Sheffield CSR (Competitor - Stress tolerator - Ruderal) scheme and its "Integrated Screening Program" (e.g. \citealt{grime1979plant, Grime:1997wm}). Meanwhile partitioning of seedling RGR into its components showed that specific leaf area (SLA = 1/leaf mass per area LMA) was typically the strongest source of variation between species \citep{Poorter:1989tx}. From the 1990s a new style of "trait ecology" arose whereby measurable traits including SLA were used directly as strategy axes \citep{Westoby:1998ug,Weiher:1999js, Westoby:2002ft}. An approach via measurable traits made broad comparisons possible across continents and latitudes and thousands of species. Traits have been seen as constructive approaches to understanding plant growth strategies \citep{Grime:1977kc,Chapin:1980gz}, community composition \citep{Lavorel:2002ff,Shipley:2006ie}, global vegetation dynamics \citep{Scheiter:2013ed} and ecosystem processes \citep{Lavorel:2002ff}.

Currently two main spectra of variation are widely cited as underpinning differences between species in vegetative growth rates. The `leaf economic spectrum' \citep{Wright:2004jb} and the 'wood economic spectrum' \citep{Chave:2009iy} reflect tissue construction costs (for specific leaf area and for wood volume respectively) trading off with tissue turnover rates or mortality risks. It has been widely expected that species with low tissue construction cost will typically have fast growth rates at least in favourable physical environments (e.g. \citealt{MullerLandau:2004dc,Wright:2004jb,Poorter:2006kw,Poorter:2008iu,Chave:2009iy,Larjavaara:2010bn,Iida:2012jb,Paine:2015df}). Yet a growing number of empirical studies indicate the correlation between traits and growth is not as consistent as that. Consider SLA as an illustration. Species with high SLA can deploy more canopy area for a given dry mass investment in leaves \citep{Poorter:1999wd, Reich:1992wm}. In addition, SLA is correlated with high photosynthetic rates and high nitrogen (N) or phosphorus concentrations in the leaf \citep{Wright:2004jb}. For seedling relative growth rates under favourable conditions, high SLA has repeatedly been found to be a strong predictor regardless of vegetation type or growth form \citep{Lambers:1992bj,Reich:1992wm,Grime:1997wm,Poorter:1999wd,Wright:1999ds}. Yet for adult plants, this correlation appears weaker or absent \citep{coomes_comparison_1998,Poorter:2008iu,Aiba:2009ft,Easdale:2009gv,Wright:2010tp}. The growing discrepancy between theoretical expectation and empirical results has led some to question whether traits are even useful for understanding growth \citep{Wright:2010tp, Paine:2015df}.

Meanwhile the possibility has been raised that trait-growth correlations may change systematically with size \citep{Iida:2014ep,Iida:2014hq,Ruger:2012jv,Falster:2011ii}.Recent theory suggests that the absence of a correlation between SLA and growth at larger sizes may be expected, when  potential influences of traits on plant function are considered \citep{Falster:2011ii, falster:2013} (Appendix \ref{app:growth}). At larger sizes the low-cost deployment benefits of high SLA may be offset or even outweighed by the high costs of rapid leaf turnover.

@@

As plants approach maximum height they increasingly divert energy away from growth and into reproduction (see \citealt{Wenk:2014jz, Falster:2011ii,Thomas:1996do}). For seedlings, where all individuals are investing solely in growth, we expect no influence of Hmax on growth. As plants become larger, species with smaller Hmax are expected to be allocating more to reproduction and less to growth, because at any given size they are closer to their Hmax.

@@

We aimed to identify studies that measured the correlation between a functional trait and a growth measurement, and searched for relevant studies using a three step procedure. First, we identified traits for which a substantial number of studies would be available, using a literature snapshot in Web of Science. While Web of Science guarantees a relatively stable and reproducible search environment, with clearly defined lists of indexed journals, its searches are restricted to metadata, such as title, keywords and abstracts \citep{Falagas:2008gtb,Beckmann:2012hn}. This limitation does not apply to Google Scholar, where, theoretically, all text that is electronically available on the Internet will be indexed. Thus, our second step was to systematically read documents returned by Google scholar for a restricted set of traits. Finally, we identified and recorded other possible data sources using our own knowledge as researchers in the field. (This included adding data from an as-yet unpublished study by Gleason et al). The complete list of studies where we inspected the full text is given in Appendix \ref{app:supp_info_files}.

@@

Each study had to meet some basic criteria to be included in our analysis. We restricted our meta-analysis to documents reporting: i) the relationship between growth and trait as a correlation coefficient, ii) the sample size and the number of species used to perform the correlation, and iii) the size/stage of plants. Where available we also recorded the geographic coordinates, number of sites, experiment type (greenhouse, field experiment, forest, shade-house etc.), growth measure (relative or absolute growth rate measured using plant diameter, height or mass), vegetation type, life form (tree, woody or mixed with herbaceous species etc.), biological scale (interspecific, intraspecific or intragenus), and experimental treatments (e.g.~fertilization, shade, salt stress). Ultimately data was included from 108 different studies \citep{Aiba:1997ho, Aiba:2009ft, Antunez:2001gk, Atkin:1998in, augspurger_light_1984, baltzer_physiological_2007, baraloto_differential_2006, baraloto_seed_2005, Bloor:2003fa, Bohlman:2006eo, Broncano:1998ck, Brown:1996ks, Bruhn:2000jz, Cai:2007ie, CamaraZapata:2003df, CastroDiez:1998gz, CastroDiez:2003jd, Cernusak:2008ds, Chao:2008hg, Chaturvedi:2011jx, Chave:2009iy, Cochard:2007bn, Coley:1983hk, Comas:2002wt, Comas:2004jza, coomes_comparison_1998, coomes_greater_2009, cornelissen_seedling_1996, Cornelissen:1997fd, Cornelissen:1998ta, Dalling:2004gs, DeBell:1994ix, Easdale:2009gv, fan_hydraulic_2012, Fayolle:2012bx, Fujimoto:2006fg, Galmes:2005fa, gleeson_plant_1994, grotkopp_toward_2002, Grubb:1996kr, Herault:2011dd, Huante:1995fd, Huante:1995tl, Huante:1998bk, HUNT:1997ge, Iida:2014ep, Iida:2014hq, king_influence_1994, king_tree_2005, King:2006dg, King:2006he, Kitajima:1994ez, Kohyama:2003dk, Kruger:2006fq, Lamers:2006dl, LopezIglesias:2014dk, Loveys:2002hj, Lusk:1997ga, Lusk:2002fma, Lusk:2013bq, Lusk:2013hz, MartinezVilalta:2010iq, McCormack:2012ch, Moya:2008ep, MullerLandau:2004dc, Nascimento:2005kl, Osone:2008dr, Osunkoya:1994ip, Osunkoya:2010ef, Paz:2005kx, Poorter:1999fp, Poorter:2001fj, Poorter:2006vb, Poorter:2008iu, Poorter:2010co, Popma:1988tv, Prior:2004cv, Read:2011du, Reich:1998ir, Reich:1998ja, Reich:1998vb, Rossatto:2009gq, RuizRobleto:2005hc, Sack:2004hm, saldana-acosta_seedling_2009, SalgadoLuarte:2012ci, Saverimuttu:1996ih, Schulze:2006ww, Shen:2014fw, Shipley:2002fs, Stratton:2001ck, Thomas:1996do, Tjoelker:1999gp, Tobner:2013cv, Tomlinson:2014im, Veneklaas:2002dt, Villagra:2013do, walters_are_1996, Walters:1993eu, Walters:1993hf, Warren:2005bc, Westbrook:2011ja, Wright:1999ds, Wright:2000kw, Wright:2001gb, Wright:2003kb, Wright:2010tp, Zhang:1995bh}.

@@

We tested size/stage effect on traits for which \textgreater{}20 correlation coefficients across at least two stages were recorded. We used a mixed-effect model of meta-analysis, in which it is assumed that studies within a stage share a common mean effect but that there is also random variation among studies in a stage, in addition to sampling variation. This random effect allows us to account for the heterogeneity among studies (e.g.~experimental type, vegetation type, error, etc.). For each trait, we established if stage could explain variance in the coefficient correlation by comparing models with the stage variable to the null model using log-likelihood ratios  \citep{Srivastava:2009we}. If the log-likelihood test returned a significant p-value, the stage model fitted the data better than the null model. Effects of other variables (vegetation type, experiment type and growth measurement) were also tested individually (results shown in the Fig. \ref{FigA7}). Estimates of the effect size for each stage were considered significant if the 95\% confidence intervals did not overlap with zero. In the case of multiple comparisons within a study, we used the method proposed by \citet{Borenstein:2009um}: we calculated the mean correlation coefficient by trait and by study, and re-calculated the effect size (see \citealt{Pere:2013gr}). Finally, we checked the dataset for publication bias with funnel plots (\citealt{Koricheva:2013tz}, Fig. \ref{FigA8}). A publication bias toward significant results creates an asymmetric funnel with small studies with non-significant effects missing from the mouth of the funnel on the side opposite to the true effect. In addition, to avoid publication bias due to selective reporting of significant results within published articles (e.g.~particular case of a `failure to publish bias' see \citealt{Jennions:2013ta}), we asked the authors for additional information when they reported a non-significant correlation between growth and trait without reporting an r value. All meta-analyses were conducted with R software \citep{Ralanguageanden:2014wf}.

@@

% * <ian.wright@mq.edu.au> 2015-04-29T07:20:39.057Z:
%
% did all these authors really report that GR-SLA relationships diminish in strength with plant size? That is how it reads, but I don't think that's true???
%

%% Anais:
% wright et al 2010 "There is a strong negative relationship between LMA and early seedling growth rates; however, direct limitation of growth rates by large LMA decreases in importance as trees mature and leaf number increases (Lambers and Poorter 1992, Reich et al. 1992, Poorter et al. 2009).

% Poorter et al 2008: "Specific leaf area may be important for the performance of small plants, as leaf removal has a large impact on their survival (e.g., Pearson et al. 2003), but less important for the performance of large trees that have substantial reserves to recuperate from photosynthetic biomass loss (Wu ̈ rth et al. 2005). Similarly, SLA may be more important for light interception of saplings for which it determines to a large extent the total leaf area and leaf area ratio, but less so for large trees, for which leaf area and light interception are largely determined by branching patterns, the number of meristems, and tree architecture (Sterck and Bongers 2001)."

% Reich et al (1992): "Leaf mass per area illustrates two of the reasons that trait–demography relationships might be inherently weak at the sapling stage. The first is ontogenetic. There is a strong negative relationship between LMA and early seedling growth rates; however, direct limitation of growth rates by large LMA decreases in importance as trees mature and leaf number increases (Lambers and Poorter 1992, Reich et al. 1992, Poorter et al. 2009)."

%

@@

Meta-analysis showed a positive correlation between Hmax and growth for adult stage, but not for saplings and juveniles. The trend for tall stature species to grow faster at a given tree size than small stature species has been noted across several tree size classes and forest types \citep{Kohyama:2003dk,Poorter:2008iu,MartinezVilalta:2010iq,Wright:2010tp,Herault:2011dd,Ruger:2012jv, Iida:2014ep}. In \citet{Wright:2010tp}, Hmax was considered as the weakest predictor of growth rates of saplings; however it was the strongest predictor of growth rates of large trees. \citet{Poorter:2008iu} speculated that the Hmax-RGR relationship among large trees might arise from including small tree species with maximum size not much larger than the  10cm dbh lower threshold used to define large trees. In our growth equations, Hmax affects growth via the fraction of energy diverted to reproduction. At a given tree size, species closer to their Hmax are expected to be allocating relatively less to vegetative growth. However this applies only at sizes where some of the species have begun to reproduce, and should not affect sapling and juvenile growth rates.

@@

\section*{Acknowledgements}\label{Acknowledgment}

@@

\begin{figure}[htbp]
\centering
\includegraphics{output/Fig1.pdf}
\caption{\textbf{Number of correlations between trait and growth for each plant stage recorded in our dataset.} Shown here are 'complete dataset' (recorded at both interspecific and intraspecific level, under unstressed and stressed conditions). Bar colors: red for adult stage, orange for sapling, grey for juvenile. Aarea (or Amass) = rate of $CO_{2}$ assimilation per unit leaf area (or leaf mass) = maximum photosynthetic rate, Hmax= asymptotic maximum height,  Ks =stem hydraulic conductance, LA = leaf area, LMR = leaf mass ratio, NARarea (or NARmass) = net mass assimilation rate per unit of leaf area (or leaf mass), Nmass (or Narea) = nitrogen content per unit of leaf mass (or leaf area), Pmass = phosphorus content per unit of leaf mass, SA/LA = sapwood area per leaf area, SLA = specific leaf area, thickness = leaf thickness, Vessel size = stem conduit size, vessel density = stem conduit density, WD = wood density}
\label{Fig1}
\end{figure}

\begin{figure}[htbp]
\centering
\includegraphics{output/Fig2.pdf}
\caption{\textbf{The relationship between growth rates and SLA or seed mass changes with plant stage.} Plots show the effect size (+ 95\%CI) of the correlation between growth rate and five functional traits for plant stage comparisons. \textbf{a)} Specific leaf area (SLA), \textbf{b)} Wood density (WD), \textbf{c)} Asymptotic height (Hmax) \textbf{d)} Seed mass and \textbf{e)} Assimilation rate of CO2 (Aarea). Effect size is a standardized measure of the deviation of the correlation coefficient from zero (Fisher's z-transformed). Effects are significant if confidence intervals (+ 95\%CI) for a given stage do not overlap with zero.  Black symbols for "ideal" data (using only interspecific correlations, growth under control conditions), grey symbols using "complete" data (see Methods for further explanation). 'n' indicates number of correlations contributing to each effect. Likelihood Ratio Tests (LRT, for ideal data only) compared maximum-likelihood fits between a pooled model and one separated by stage. If the LRT returned a significant p-value, the stage model fitted the data better than the null model.
}
\label{Fig2}

@@

We adapted growth equations from \cite{Falster:2011ii} and \cite{falster:2013} to generate hypotheses on both absolute and relative growth rates in biomass (b, eqn \ref{eq:eq1}), height (H, eqn \ref{eq:eq2}) and diameter (D, eqn \ref{eq:eq4}). These size dimensions are measured on seedling and adult plants. Here we provide a brief overview of the model; an upcoming publication will elaborate further on the predicted relationships between traits and growth rate.

Let $m_i$ denote the mass, $r_i$ the mass-specific respiration rate, and $k_i$ the turnover rate of different plant tissues, with the subscripts $i=l,s,r,t$ referring to leaves, sapwood and bark, roots, and total plant. Similarly let $a_i$ denote areas, of leaves ($i=l$) and of cross-sections of total stem, sapwood and heartwood ($i= st,ss,sh$) respectively.

>>>>

\documentclass[a4paper]{article}\usepackage[]{graphicx}\usepackage[]{color}
\usepackage{alltt}
\usepackage{amssymb,amsmath}
\usepackage{palatino}
\usepackage{framed}
\usepackage{parskip}
\usepackage{graphicx}
\usepackage{fixltx2e}
\usepackage[default,osfigures,scale=0.95]{opensans}
\usepackage{geometry}
\usepackage{longtable}
\usepackage{authblk}
\usepackage[colorinlistoftodos]{todonotes}
\geometry{verbose,tmargin=2cm,bmargin=2cm,lmargin=2cm,rmargin=2.5cm}
\linespread{2}
\usepackage{hyperref}

@@

@@

\textit{Statement of authorship} MW, DF, IW, AG designed the study, IW and DF provided their bibliography database, AG and EG searched and collected the data, AG performed the meta-analyses, DF performed modeling work, AG wrote the first draft, MW improved substantially the manuscript, and all authors contributed to revisions.

\textit{Keywords (8/10)} asymptotic maximum height, maximum photosynthetic rate, plant ontogenetic stage, plant functional traits, plant growth strategy, seed mass, specific leaf area, wood density

\textit{Type of article} Letters

\textit{Number of words in the abstract} 148

\textit{Number of words in the main text (excluding abstract, acknowledgements, references, table and figure legends)} 4566/5000

\textit{Number of words in each text box} 0

\textit{Number of general references} 50

\textit{Number of data source references} 108

\textit{Number of figures} 2

\textit{Number of tables} 0

\textit{Number of text boxes} 0

\textit{corresponding author} Anais Gibert, anais.gibert@gmail.com, Dept of Biological Sciences, Macquarie University, Sydney, NSW 2109, Australia, tel: +61 2 9850 8194

\todo[inline,color=white]{1. need to delete references 50/50: DONE}

@@

\todo[inline,color=white]{3. the bibliography style needs to be changed to fit with the new style of Ecology letters: journal abbreviation: DONE}

\todo[inline, color=white] {4.  re write Appendix A growth equation : DONE}

\todo[inline, color=white] {5. to write a "Read.me" file for the dataset/guithub: DONE}

\todo[inline, color=white] {6. to add the list of traits/stage categories combination for which we identified a need of more data in the last paragraph of the discussion: DONE}

@@

\todo[inline, color=white] {8. list of preferred and non preferred reviewers, to list any editorial board members with whom one of the authors is in conflict: see the list \href{here}{http://onlinelibrary.wiley.com/journal/10.1111/(ISSN)1461-0248/homepage/EditorialBoard.html}}

\todo[inline, color=white] {9. To add asterisk in front of the data-source references and cites them in the text}

\todo[inline, color=white] {10. To delete discussion about references in coverletter: DONE}

\todo[inline, color=white] {11. To add a clear statment in cover letter of how exactely the enclosed work is outstandingly novel relative to recent work by the author and co authors cited in the present submission}

\todo[inline, color=white] {12. to check the number of word in figures legends (less than 150): DONE}

@@

The phrase "plant ecological strategy" refers to how species face the challenge they all share:  to acquire sufficient water, nutrients and light for individual growth and to live long enough to replace themselves with offspring. An idea that strategy differences might involve fast vs slow growth goes back at least to Grime and Hunt \citeyearpar{Grime:1975gr}, who measured a wide spread of relative growth rates for seedlings during early exponential growth under favourable conditions. Seedling potential RGR has continued to be used as a major strategy indicator within the Sheffield CSR (Competitor - Stress tolerator - Ruderal) scheme and its "Integrated Screening Program" (e.g. \citealt{grime1979plant, Grime:1997wm}). Meanwhile partitioning of seedling RGR into its components showed that specific leaf area (SLA = 1/leaf mass per area LMA) was typically the strongest source of variation between species \citep{Poorter:1989tx}. From the 1990s a new style of "trait ecology" arose whereby measurable traits including SLA were used directly as strategy axes \citep{Westoby:2002ft}. An approach via measurable traits made broad comparisons possible across continents and latitudes and thousands of species. Traits have been seen as constructive approaches to understanding plant growth strategies \citep{Grime:1977kc,Chapin:1980gz}, community composition \citep{Lavorel:2002ff,Shipley:2006ie}, global vegetation dynamics \citep{Scheiter:2013ed} and ecosystem processes \citep{Lavorel:2002ff}.

Currently two main spectra of variation are widely cited as underpinning differences between species in vegetative growth rates. The `leaf economic spectrum' \citep{Wright:2004jb} and the 'wood economic spectrum' \citep{Chave:2009iy} reflect tissue construction costs (for specific leaf area and for wood volume respectively) trading off with tissue turnover rates or mortality risks. It has been widely expected that species with low tissue construction cost will typically have fast growth rates at least in favourable physical environments (e.g. \citealt{MullerLandau:2004dc,Wright:2004jb,Poorter:2008iu,Chave:2009iy,Larjavaara:2010bn,Iida:2012jb,Paine:2015df}). Yet a growing number of empirical studies indicate the correlation between traits and growth is not as consistent as that. Consider SLA as an illustration. Species with high SLA can deploy more canopy area for a given dry mass investment in leaves \citep{Poorter:1999wd, Reich:1992wm}. In addition, SLA is correlated with high photosynthetic rates and high nitrogen (N) or phosphorus concentrations in the leaf \citep{Wright:2004jb}. For seedling relative growth rates under favourable conditions, high SLA has repeatedly been found to be a strong predictor regardless of vegetation type or growth form \citep{Lambers:1992bj,Reich:1992wm,Grime:1997wm,Poorter:1999wd,Wright:1999ds}. Yet for adult plants, this correlation appears weaker or absent \citep{coomes_comparison_1998,Poorter:2008iu,Aiba:2009ft,Easdale:2009gv,Wright:2010tp}. The growing discrepancy between theoretical expectation and empirical results has led some to question whether traits are even useful for understanding growth \citep{Wright:2010tp, Paine:2015df}.

Meanwhile the possibility has been raised that trait-growth correlations may change systematically with size \citep{Iida:2014ep,Iida:2014hq,Ruger:2012jv,Falster:2011ii}.Recent theory suggests that the absence of a correlation between SLA and growth at larger sizes may be expected, when  potential influences of traits on plant function are considered \citep{Falster:2011ii, falster:2013} (see Appendix \ref{app:growth} in Supporting Informations). At larger sizes the low-cost deployment benefits of high SLA may be offset or even outweighed by the high costs of rapid leaf turnover.

@@

As plants approach maximum height they increasingly divert energy away from growth and into reproduction (see \citealt{Thomas:1996do, Falster:2011ii, Wenk:2014jz}). For seedlings, where all individuals are investing solely in growth, we expect no influence of Hmax on growth. As plants become larger, species with smaller Hmax are expected to be allocating more to reproduction and less to growth, because at any given size they are closer to their Hmax.

@@

We aimed to identify studies that measured the correlation between a functional trait and a growth measurement, and searched for relevant studies using a three step procedure. First, we identified traits for which a substantial number of studies would be available, using a literature snapshot in Web of Science. While Web of Science guarantees a relatively stable and reproducible search environment, with clearly defined lists of indexed journals, its searches are restricted to metadata, such as title, keywords and abstracts \citep{Beckmann:2012hn}. This limitation does not apply to Google Scholar, where, theoretically, all text that is electronically available on the Internet will be indexed. Thus, our second step was to systematically read documents returned by Google scholar for a restricted set of traits. Finally, we identified and recorded other possible data sources using our own knowledge as researchers in the field. (This included adding data from an as-yet unpublished study by Gleason et al). The complete list of studies where we inspected the full text is given in Appendix \ref{app:supp_info_files}.

@@

Each study had to meet some basic criteria to be included in our analysis. We restricted our meta-analysis to documents reporting: i) the relationship between growth and trait as a correlation coefficient, ii) the sample size and the number of species used to perform the correlation, and iii) the size/stage of plants. Where available we also recorded the geographic coordinates, number of sites, experiment type (greenhouse, field experiment, forest, shade-house etc.), growth measure (relative or absolute growth rate measured using plant diameter, height or mass), vegetation type, life form (tree, woody or mixed with herbaceous species etc.), biological scale (interspecific, intraspecific or intragenus), and experimental treatments (e.g.~fertilization, shade, salt stress). Ultimately data was included from 108 different studies \citep{Aiba:1997ho, Aiba:2009ft, Antunez:2001gk, Atkin:1998in, augspurger_light_1984, baltzer_physiological_2007, baraloto_differential_2006, baraloto_seed_2005, Bloor:2003fa, Bohlman:2006eo, Broncano:1998ck, Brown:1996ks, Bruhn:2000jz, Cai:2007ie, CamaraZapata:2003df, CastroDiez:1998gz, CastroDiez:2003jd, Cernusak:2008ds, Chao:2008hg, Chaturvedi:2011jx, Chave:2009iy, Cochard:2007bn, Coley:1983hk, Comas:2002wt, Comas:2004jz, coomes_comparison_1998, coomes_greater_2009, cornelissen_seedling_1996, Cornelissen:1997fd, Cornelissen:1998ta, Dalling:2004gs, DeBell:1994ix, Easdale:2009gv, fan_hydraulic_2012, Fayolle:2012bx, Fujimoto:2006fg, Galmes:2005fa, gleeson_plant_1994, grotkopp_toward_2002, Grubb:1996kr, Herault:2011dd, Huante:1995fd, Huante:1995tl, Huante:1998bk, HUNT:1997ge, Iida:2014ep, Iida:2014hq, king_influence_1994, king_tree_2005, King:2006dg, King:2006he, Kitajima:1994ez, Kohyama:2003dk, Kruger:2006fq, Lamers:2006dl, LopezIglesias:2014dk, Loveys:2002hj, Lusk:1997ga, Lusk:2002fma, Lusk:2013bq, Lusk:2013hz, MartinezVilalta:2010iq, McCormack:2012ch, Moya:2008ep, MullerLandau:2004dc, Nascimento:2005kl, Osone:2008dr, Osunkoya:1994ip, Osunkoya:2010ef, Paz:2005kx, Poorter:1999fp, Poorter:2001fj, Poorter:2006vb, Poorter:2008iu, Poorter:2010co, Popma:1988tv, Prior:2004cv, Read:2011du, Reich:1998ir, Reich:1998ja, Reich:1998vb, Rossatto:2009gq, RuizRobleto:2005hc, Sack:2004hm, saldana-acosta_seedling_2009, SalgadoLuarte:2012ci, Saverimuttu:1996ih, Schulze:2006ww, Shen:2014fw, Shipley:2002fs, Stratton:2001ck, Thomas:1996do, Tjoelker:1999gp, Tobner:2013cv, Tomlinson:2014im, Veneklaas:2002dt, Villagra:2013do, walters_are_1996, Walters:1993eu, Walters:1993hf, Warren:2005bc, Westbrook:2011ja, Wright:1999ds, Wright:2000kw, Wright:2001gb, Wright:2003kb, Wright:2010tp, Zhang:1995bh}.

@@

We tested size/stage effect on traits for which \textgreater{}20 correlation coefficients across at least two stages were recorded. We used a mixed-effect model of meta-analysis, in which it is assumed that studies within a stage share a common mean effect but that there is also random variation among studies in a stage, in addition to sampling variation. This random effect allows us to account for the heterogeneity among studies (e.g.~experimental type, vegetation type, error, etc.). For each trait, we established if stage could explain variance in the coefficient correlation by comparing models with the stage variable to the null model using log-likelihood ratios \citep{Zuur:2009cfa}. If the log-likelihood test returned a significant p-value, the stage model fitted the data better than the null model. Effects of other variables (vegetation type, experiment type and growth measurement) were also tested individually (results shown in the Fig. \ref{FigA7}). Estimates of the effect size for each stage were considered significant if the 95\% confidence intervals did not overlap with zero. In the case of multiple comparisons within a study, we used the method proposed by \citet{Borenstein:2009um}: we calculated the mean correlation coefficient by trait and by study, and re-calculated the effect size. Finally, we checked the dataset for publication bias with funnel plots (\citealt{Koricheva:2013tz}, Fig. \ref{FigA8}). A publication bias toward significant results creates an asymmetric funnel with small studies with non-significant effects missing from the mouth of the funnel on the side opposite to the true effect. In addition, to avoid publication bias due to selective reporting of significant results within published articles (e.g.~particular case of a `failure to publish bias' see \citealt{Jennions:2013ta}), we asked the authors for additional information when they reported a non-significant correlation between growth and trait without reporting an r value. All meta-analyses were conducted with R software \citep{Ralanguageanden:2014wf}.

@@

@@

Meta-analysis showed a positive correlation between Hmax and growth for adult stage, but not for saplings and juveniles. The trend for tall stature species to grow faster at a given tree size than small stature species has been noted across several tree size classes and forest types (e.g. \citealt{Poorter:2008iu,Wright:2010tp,Herault:2011dd,Ruger:2012jv,Iida:2014ep}). In \citet{Wright:2010tp}, Hmax was considered as the weakest predictor of growth rates of saplings; however it was the strongest predictor of growth rates of large trees. \citet{Poorter:2008iu} speculated that the Hmax-RGR relationship among large trees might arise from including small tree species with maximum size not much larger than the  10cm dbh lower threshold used to define large trees. In our growth equations, Hmax affects growth via the fraction of energy diverted to reproduction. At a given tree size, species closer to their Hmax are expected to be allocating relatively less to vegetative growth. However this applies only at sizes where some of the species have begun to reproduce, and should not affect sapling and juvenile growth rates.

@@

\section*{Acknowledgments}\label{Acknowledgment}

@@

\begin{figure}[htbp]
\centering
\includegraphics{output/Fig1.pdf}
\caption{\textbf{Number of correlations between trait and growth for each plant stage recorded in our dataset.} Shown here are 'complete dataset' (recorded at both interspecific and intraspecific level, under unstressed and stressed conditions). Bar colors: red for adult, orange for sapling, grey for juvenile. Aarea (or Amass) = rate of $CO_{2}$ assimilation per unit leaf area (or leaf mass) = maximum photosynthetic rate, Hmax= asymptotic maximum height,  Ks =stem hydraulic conductance, LA = leaf area, LMR = leaf mass ratio, NARarea (or NARmass) = net mass assimilation rate per unit of leaf area (or leaf mass), Nmass (or Narea) = nitrogen content per unit of leaf mass (or leaf area), Pmass = phosphorus content per unit of leaf mass, SA/LA = sapwood area per leaf area, SLA = specific leaf area, thickness = leaf thickness, Vessel size = stem conduit size, vessel density = stem conduit density, WD = wood density}
\label{Fig1}
\end{figure}

\begin{figure}[htbp]
\centering
\includegraphics{output/Fig2.pdf}
\caption{\textbf{The relationship between growth rates and SLA or seed mass changes with plant stage.} Plots show the effect size (+ 95\%CI) of the correlation between growth rate and five functional traits for plant stage comparisons. \textbf{a)} Specific leaf area (SLA), \textbf{b)} Wood density (WD), \textbf{c)} Asymptotic height (Hmax) \textbf{d)} Seed mass and \textbf{e)} Assimilation rate of CO2 (Aarea). Effect size is a standardized measure of the deviation of correlation coefficient from zero (Fisher's z-transformed). Effects are significant if confidence intervals (95\%CI) for a given stage do not overlap with zero. Black point: ideal data (at interspecific level \& under unstressed conditions), grey points: all the data. 'n' indicates number of correlations contributing to each effect. Likelihood Ratio Tests (LRT, for ideal data only) compared maximum-likelihood fits between a pooled model and one separated by stage. A significant p-value means the stage model fitted the data better than the null model.
}
\label{Fig2}

@@

We adapted growth equations from \cite{Falster:2011ii} and \cite{falster:2013} to generate hypotheses on both absolute and relative growth rates in biomass ($m_t$, eqn \ref{eq:eq1}), height (H, eqn \ref{eq:eq2}) and diameter (D, eqn \ref{eq:eq4}). These size dimensions are routinely measured on seedling and adult plants. Here we provide a brief overview of the model; an upcoming publication will elaborate further on the predicted relationships between traits and growth rate.

Let $m_i$ denote the mass, $r_i$ the mass-specific respiration rate, and $k_i$ the turnover rate of different plant tissues, with the subscripts $i=l,s,r,t$ referring to live biomass in leaves, sapwood and bark, roots, and in the plant. Similarly let $a_i$ denote areas, of leaves ($i=l$) and of cross-sections of total stem and sapwood ($i= st,ss$) respectively.

The rate at which live biomass originating from the plant $b$ changes is given by
\begin{equation}\label{eq:eq0}
\underbrace{\frac{db}{dt}}_{\text{net live biomass production}} = \underbrace{y}_{\text{yield}}  \big(\underbrace{a_{l} A_{\textrm{area}}}_{\text{photosynthesis}} - \underbrace{\sum_{i=l,s,r} m_{i} r_{i}}_{\text{respiration}}\big) - \underbrace{ \sum_{i=l,s,r} m_{i} k_{i}}_{\text{turnover}},
\end{equation}
where $y$ is the fraction of assimilated carbon fixed into biomass,  and  $A_{\textrm{area}}$ is the assimilation rate of CO$_{2}$ per leaf area. The rate at which live biomass is accumulated on the plant is then

\begin{equation}\label{eq:eq1}
\underbrace{\frac{dm_t}{dt}}_{\text{growth in live biomass}} = \underbrace{\frac{dm_t}{db}}_{\text{allocation to growth}}  \times \underbrace{\frac{db}{dt}}_{\text{net live biomass production}},
\end{equation}
where allocation to growth is the fraction of biomass increase that goes to vegetative growth rather than to seed production. Height growth rate can then be expressed as
\begin{equation}\label{eq:eq2}
\underbrace{\frac{dH}{dt}}_{\text{growth rate in height}} = \underbrace{\frac{dH}{da_{l}}}_{\text{architecture layout}} \times \underbrace{\frac{da_{l}}{dm_{t}}}_{\text{leaf deployment per mass}} \times \frac{dm_t}{db} \times \frac{db}{dt}. 
\end{equation}
Similarly basal area growth can be expressed as
\begin{equation}\label{eq:eq3}
\underbrace{\frac{da_{st}}{dt}}_{\text{basal area increment}} = \underbrace{\frac{da_{ss}}{da_{l}}}_{\text{sapwood area per leaf area}} \times \frac{da_{l}}{dm_{t}} \times\frac{dm_t}{db} \times\frac{db}{dt} +  \underbrace{ k_{s} a_s }_{\text{sapwood turnover}}.
\end{equation}
